Title

### 2015-12-09 paper/paper.tex
add content for greedy search and annealing

\usepackage{amsmath}
\usepackage{cite}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\tableofcontents
\pagebreak

@@

\subsection{Discrete Optimizations}

>>>>

\usepackage[section]{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{graphicx}

@@

\begin{document}
\maketitle
\tableofcontents
\listofalgorithms
\pagebreak

@@

\subsection{Discrete Optimization}

In both subproblems, we trained classifiers which assign a score to how ``good"
an instance is with regard to that problem. So, to find the best instance, we
could just enumerate all possible permutations or combinations of the input,
and select the instance which maximizes (or, in the case of subgraph ordering,
minimizes) the classifier's score. However, in the case of subgraph selection,
for a paragraph of $n$ facts, there are $O(2^n)$ possible partitions. In the
case of subgraph ordering, for a paragraph of $n$ sentences, there are $O(n!)$
possible orderings. Neither of these are very computationally efficient, so we
perform discrete optimization to approach an optimal solution, rather than
enumerating all possible inputs. It is worth noting that in practice, this is
more of a problem for the subgraph selection module, since the partitions
returned by the subgraph selector are generally not too large, so $n$ for the
subgraph orderer is not too bad.

For discrete optimization, we implemented a greedy search procedure as follows:
\begin{algorithm}
\caption{Greedy search procedure}
\label{greedy_search_alg}
\begin{algorithmic}
\STATE Input: $s$ // start state \\
\STATE Input: $classifier$ \\
\STATE $Q \gets [s]$ // queue of states to visit \\
\STATE $opt, optv, oldoptv \gets null, 0, 1$
\WHILE{$Q\neq\emptyset$ and $optv \neq oldoptv$}
    \STATE $S \gets \{s: s \in Q \}$
    \STATE $Q \gets \emptyset$
    \STATE $oldoptv \gets optv$
    \FORALL{$s \in S$}
        \STATE $N \gets neighbors(s)$\\
        \STATE Add all elements of $N$ to $Q$\\
        \IF{$classifier.score(s) > optv$}
            \STATE $opt, optv \gets s, classifier.score(s)$\\
        \ENDIF
    \ENDFOR
\ENDWHILE
\end{algorithmic}
\end{algorithm}

Additionally, we used a simmulated annealing approach, but only for the
subgraph ordering problem.
